Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
reorganise some sections
rename some titles
refer to detailed iptables configuration tutorial

@@

\section{Optimizing configuration with an example setup}
\subsection{Example definition}
\begin{itemize}
  \item A web service should be available from all networks (i.e. internet) on port 80 (http) and 443 (https)
  \item The server can be managed remotely using SSH (port 22) and a webbased admin tool (port 10000), but only from a limited set of IP addresses (admin PC's).
  \item The server hosts a samba service (several TCP ports), that should only be available from a limited set of IP addresses (admin + webmaster PC's).
  \item Outgoing connections will be filtered, but some services should be allowed (DNS, DHCP, SMTP, NTP) and some external websites should be available to get updates.
\end{itemize}

@@

\subsubsection{icmp in chain}

@@

\subsubsection{admin IP chain}

@@

\subsubsection{webmaster IP chain}

@@

\subsubsection{external websites chain}

>>>>

\subsection{More about iptables}
This was just a brief introduction to iptables/netfilter. If you want to know more about iptables configuration, you can have a look at this excelent and detailed tutorial : http://www.frozentux.net/iptables-tutorial/iptables-tutorial.html
\newpage

\section{Optimizing configuration}
\subsection{Example setup definition}
\begin{itemize}
  \item A web service should be available from all networks (i.e. internet) on port 80 (http) and 443 (https)
  \item The server can be managed remotely using SSH (port 22) and a webbased admin tool (port 10000), but only from a limited set of IP addresses (admin PC's).
  \item The server hosts a samba service (several TCP ports), that should only be available from a limited set of IP addresses (admin + webmaster PC's).
  \item Outgoing connections will be filtered, but some services should be allowed (DNS, DHCP, SMTP, NTP) and some external websites should be available to get updates.
\end{itemize}

@@

@@

\subsubsection{ICMP chain}

@@

\subsubsection{admin chain}

@@

\subsubsection{webmaster chain}

@@

\subsubsection{External websites chain}
